{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-08-24 ident_manu.Rnw
senstab1 senstab2 gone, senstab now all cats by state var

<<dosens, eval = T, cache = F>>=
load(file = 'data/sens_ests_cat_all.RData')
load(file = 'data/sens_ests_all.RData')

# subset the sensitivy and sensitivity catgory lists
tmpest <- sens_ests_all[['O2']]
tmpest_cat <- sens_ests_cat_all[['O2']]

labs <- parcats2(as_df = TRUE) %>% 
  rename(Parameter = shrt)

totab <- tmpest_cat %>% 
  select(Parameter) %>% 
  left_join(., tmpest$sens, by = 'Parameter') %>% 
  left_join(., labs, by = 'Parameter') %>% 
  select(cats, lngs, Parameter, vals, L1) %>% 
  arrange(cats, -L1) %>% 
  mutate(
    Parameter = par_txt(Parameter),
    lngs = gsub('^.*:\\s', '', lngs), 
    lngs = gsub('_', '', lngs), 
    vals = sapply(vals, scinot),
    L1 = sapply(L1, scinot, digits = 2, pow = 2)
  ) %>% 
  rename(
    Description = lngs, 
    Value = vals
  )

# final table formatting
Description <- totab$Description
cats <- totab$cats
totab <- totab[,-c(1:2)]

cap.val<- paste('Sensitivities of \\ac{do} to perturbation of indivividual parameters.  Sensitivities are based on a 50\\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \\cref{l1}).  Parameters that did not affect \\ac{do} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.')

latex( 
  totab,
  file = '',
  rowlabel = 'Description',
  caption = cap.val,
  caption.loc = 'top',
  rowname = Description,
  rgroup = unique(cats),
  n.rgroup = as.numeric(table(cats)),
  size = 'footnotesize',
  label = 'tab:dosens'
  )
@

>>>>

% do sensitivity all categories
<<dosens, eval = T, cache = F>>=
senstab(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', digits = 2, pow = 2, tabsize = 'footnotesize')
@

### 2016-08-24 ident_manu.tex
senstab1 senstab2 gone, senstab now all cats by state var

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Tue Aug 23 17:18:33 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

% optics sensitivity

% organic matter sensitivity

% phytoplankton sensitivity

% temperature sensitivity

% zooplankton sensitivity

>>>>

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Aug 24 11:39:30 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\footnotesize
\caption{Sensitivities of \ac{do} to perturbation of indivividual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect \ac{do} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:dosens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
\hline
{\bfseries Optics}&&&\tabularnewline
~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$\tabularnewline
~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.94\times 10^{-5}$\tabularnewline
\hline
{\bfseries Temperature}&&&\tabularnewline
~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$0.92$\tabularnewline
\hline
{\bfseries Phytoplankton}&&&\tabularnewline
~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$102.96$\tabularnewline
~~maximum growth rate&\textit{umax}&$0.41$&$18.21$\tabularnewline
~~mortality coefficient&\textit{mA}&$0.1$&$1.62$\tabularnewline
~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$1.2$\tabularnewline
~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.95$\tabularnewline
~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.35$\tabularnewline
~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.16$\tabularnewline
~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.1$\tabularnewline
~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.09$\tabularnewline
~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.09$\tabularnewline
~~half-saturation constant for N&\textit{Kn}&$4.51$&$8.86\times 10^{-3}$\tabularnewline
~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$3.49\times 10^{-3}$\tabularnewline
~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$1.09\times 10^{-3}$\tabularnewline
\hline
{\bfseries Zooplankton}&&&\tabularnewline
~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$1.87\times 10^{-3}$\tabularnewline
~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$1.1\times 10^{-3}$\tabularnewline
~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1.72\times 10^{-4}$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.21\times 10^{-4}$\tabularnewline
~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$2.19\times 10^{-5}$\tabularnewline
\hline
{\bfseries Organic Matter}&&&\tabularnewline
~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.9$\tabularnewline
~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.53$\tabularnewline
~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.15$\tabularnewline
~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.11$\tabularnewline
~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.02$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$5.27\times 10^{-4}$\tabularnewline
~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$3.67\times 10^{-6}$\tabularnewline
~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$1.75\times 10^{-6}$\tabularnewline
\hline
\end{tabular}\end{center}}

\end{table}
